Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-09-12 manuscript/supplemental_material.Rnw
add placenta classification tables

\begin{table}[hb]
<<placental_classification,echo=FALSE,results="asis">>=
placental.classification <- fread("../data/placental_classification.txt")
print(xtable(placental.classification,
             display=c("s","s","s","s","s"),
             align=c("c","c","c","c","c")),
      include.rownames=FALSE,
      floating=FALSE,
      booktabs=TRUE
      )

@@

>>>>

<<placental_classification,echo=FALSE,results="hide",cache.extra=file.info(dir("../data","placenta.*classification.*",full.names=TRUE))[,"mtime"]>>=
placenta_classification <- fread("../data/placental_classification.txt")
load("../data/placenta_classification_p")
for (mf.bp in c("mf","bp")) {
    for (class in c("interdigitation","barrier","shape")) {
        load(paste0("../data/placenta_classification_go_",mf.bp,"_",class))
    }
}

\begin{table}[hb]
<<placental_classification_table,echo=FALSE,results="asis">>=
print(xtable(placental.classification,
             display=c("s","s","s","s","s"),
             align=c("c","c","c","c","c")),
      include.rownames=FALSE,
      floating=FALSE,
      booktabs=TRUE
      )

@@

\section{Placenta Classification Analyses}

<<placenta_class_table,echo=FALSE,results="hide">>=
placenta_class_table <- function(class="shape") {
    subtable <- placenta.classification.p[,c("rn",class,paste0(class,".fdr")),with=FALSE]
    setnames(subtable,c("Gene","p","FDR"))
    subtable <- head(subtable[FDR <= 0.05,][order(p),],n=50)
    print(xtable(subtable,
                 align=c("c","c","r","r"),
                 display=c("s","s","g","g")
                 ),
          booktabs=TRUE,
          floating=FALSE,
          include.rownames=FALSE,
          math.style.exponents=TRUE,
          size="\\tiny")
}

\subsection{Attachment Shape}

\begin{table}
<<attachment_shape_significant,echo=FALSE,results="asis">>=
placenta_class_table("shape")
@ 
\caption{Top 50 genes which are associated with the shape of placenta attachment}
\label{tab:shape_genes}
\end{table}

\subsection{Maternal-Fetal Intimacy}

<<intimacy_significant,echo=FALSE,results="asis">>=
placenta_class_table("barrier")
@ 
\caption{Top 50 genes which are associated with the degree of placenta intimacy}
\label{tab:barrier_genes}
\end{table}

\subsection{Maternal-Fetal Interdigitation}

<<interdigitation_significant,echo=FALSE,results="asis">>=
placenta_class_table("interdigitation")
@ 
\caption{Top 50 genes which are associated with the degree of maternal-fetal interdigitation}
\label{tab:interdigitation_genes}
\end{table}
